Type cones of $\b{g}$-vector fans

### 2019-02-21 thirdPaper/draft/typeConeAssociahedra.tex
cleaning

\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
\[
 F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
\]

@@

\begin{definition}\label{defi::bilinear form}
 For any two objects~$X$ and~$Y$ of~$\cat$, define
 \[
  \langle X, Y \rangle := \dim_{\field} \Hom{\Lambda}(FX,FY).
 \]
 This defines a bilinear form
 \[
  \langle -,-\rangle : \Ksp(\cat) \times \Ksp(\cat) \xrightarrow{} \Z.
 \]
\end{definition}

\begin{notation}\label{notation::ell_X}
\begin{enumerate}
 \item For any indecomposable object~$X$ of~$\cat$, let
 \[
  X \to E \to \susp^{-1} X \to \susp X
 \]
 be an almost split triangle (unique up to isomorphism).  We let
 \[
  \ell_X := [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
 \]

 \item For any indecomposable object~$Y$ of~$\cat$, let
 \[
  \susp Y \to E' \to  Y \to \susp^2 Y
 \]
 be an almost split triangle (unique up to isomorphism).  We let
 \[
  r_Y := [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
 \]
\end{enumerate}
\end{notation}

@@

\begin{theorem}\label{theo::relations-g-vecteurs}
 Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.  Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set~\[L:=\big\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \big\}\] generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$. 
 In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}

\begin{corollary}
 Assume that~$\ind(\cat)$ is finite.  Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.  Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\setminus \add(\susp T)$.
\end{corollary}
\begin{proof}
 We know that~$x=\sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative. 
 The functor~$F=\cat(T,-)$ induces an exact sequence
 \[
  FX \to FE \to FY \to 0,
 \]
 which in turn induces an exact sequence
 \[
  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
 \]
 Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
\end{proof}

@@

\begin{definition}
 The \defn{index} of an object~$X$ is the element
 \[
  \ind_T(X) := [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
 \]
\end{definition}

@@

\begin{lemma}\label{lemm::coefficients}
 Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat)\setminus \add(\susp T)$, we have that
 \[
  \lambda_A = \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle} = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}.
 \]
\end{lemma}
\begin{proof}
 Let~$B\in \ind(\cat) \setminus \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
 \[
  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
 \]
 The equality~$\lambda_A = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}$ is proved in a similar way.
\end{proof}

@@

 Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
 \[
  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
 \]
 Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.

@@

\begin{proposition}\label{prop::free-set}
 \begin{enumerate}
  \item The set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
  \item The set~$\{[r_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}$ is free in~$\Ksp(\cat)$.
 \end{enumerate}
\end{proposition}
\begin{proof}
 We only prove (1); the proof of (2) is similar.  Assume that~
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
 \]
 Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \setminus \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
 \[
  x = \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
 \]
 But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$.  Thus~$\lambda_i = 0$ for all~$i\in \{1, \ldots, n\}$.  This finishes the proof.
\end{proof}

\begin{proposition}
 Assume that~$\ind(\cat)$ is finite.  Then the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
\[
 z = x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
\]
Then for any~$B\in \ind{\cat}$, we have that
\[
 \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0, 
\]
where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.  Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.  This finishes the proof.
\end{proof}

\begin{corollary}
 If~$\ind(\cat)$ is finite, then the set~\[\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}\] is a basis of~$\Ksp(\cat)$.
\end{corollary}
\begin{proof}
 By Proposition~\ref{prop::free-set}, the set is free.  It suffices to prove that it generates~$\Ksp(\cat)$.  Let~$x\in \Ksp(\cat)$.  Consider
 \[
  z = x - \sum_{A\in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
 \]
 Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
\end{proof}

@@

\begin{proposition}
 Assume that the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
\end{proposition}
\begin{proof}
 Let~$x\in \ker \b g$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support.  For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.

@@

\begin{remark}
Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Proposition 4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general settup: For any~$X,Y\in\cat$,
\[
\langle X,Y\rangle := \dim_\field \Hom{\tc}(FX,FY) = \dim_\field \cat/(\susp\tc)(X,Y).
\]
\end{remark}

When this makes sense, we make use of Notation~\ref{notation::ell_X}: if
\[
X \infl E \defl Y \dashrightarrow
\]
is an almost-split sequence (see~\cite{IyamaNakaokaPalu} for a definition in this setting), we let
\[
 \ell_X := [X]+[Y]-[E]\in\Ksp(\cat).
\]

\begin{theorem}\label{theorem::extricats}
Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation. Fix a conflation~$T\to 0 \to \susp T$. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
\[
 L:=\left\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \right\}
\]
generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}

\begin{corollary}
Assume that~$\ind(\cat)$ is finite.
Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\setminus\add(\susp T)$.
\end{corollary}

>>>>

\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
\[
F = \cat(T,-): \cat \xrightarrow{} \MOD \Lambda.
\]

@@

\begin{definition}\label{defi::bilinear form}
 For any two objects~$X$ and~$Y$ of~$\cat$, define
 \[
  \langle X, Y \rangle \eqdef \dim_{\field} \Hom{\Lambda}(FX,FY).
 \]
 This defines a bilinear form
 \[
  \langle -,-\rangle : \Ksp(\cat) \times \Ksp(\cat) \xrightarrow{} \Z.
 \]
\end{definition}

\begin{notation}\label{notation::ell_X}
\begin{enumerate}
 \item For any indecomposable object~$X$ of~$\cat$, let
 \[
  X \to E \to \susp^{-1} X \to \susp X
 \]
 be an almost split triangle (unique up to isomorphism).  We let
 \[
  \ell_X \eqdef [X] + [\susp^{-1} X]  - [E] \in \Ksp(\cat).
 \]

 \item For any indecomposable object~$Y$ of~$\cat$, let
 \[
  \susp Y \to E' \to  Y \to \susp^2 Y
 \]
 be an almost split triangle (unique up to isomorphism).  We let
 \[
  r_Y \eqdef [Y] + [\susp Y]  - [E'] \in \Ksp(\cat).
 \]
\end{enumerate}
\end{notation}

@@

\begin{theorem}\label{theo::relations-g-vecteurs}
 Let~$\cat$ be a category satisying the hypotheses of Section \ref{sect::setting}.  Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
 \[
 L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
 \]
 generates the kernel of~$\b g:\Ksp(\cat) \to \Kg(\cat)$. 
 In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}

\begin{corollary}
 Assume that~$\ind(\cat)$ is finite.  Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.  Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
\end{corollary}
\begin{proof}
 We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative. 
 The functor~$F=\cat(T,-)$ induces an exact sequence
 \[
  FX \to FE \to FY \to 0,
 \]
 which in turn induces an exact sequence
 \[
  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
 \]
 Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
\end{proof}

@@

\begin{definition}
 The \defn{index} of an object~$X$ is the element
 \[
  \ind_T(X) \eqdef [T_0^X] - [T_1^X] \in \Ksp(\add(T)).
 \]
\end{definition}

@@

\begin{lemma}\label{lemm::coefficients}
 Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat) \ssm \add(\susp T)$, we have that
 \[
  \lambda_A = \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle} = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}.
 \]
\end{lemma}
\begin{proof}
 Let~$B\in \ind(\cat) \ssm \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
 \[
  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
 \]
 The equality~$\lambda_A = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}$ is proved in a similar way.
\end{proof}

@@

 Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
 \[
  x = \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
 \]
 Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.

@@

\begin{proposition}\label{prop::free-set}
 \begin{enumerate}
  \item The set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
  \item The set~$\set{[r_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \dots, n}$ is free in~$\Ksp(\cat)$.
 \end{enumerate}
\end{proposition}
\begin{proof}
 We only prove (1); the proof of (2) is similar.  Assume that~
 \[
  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \lambda_A \ell_A + \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
 \]
 Then~$\langle x, [A] \rangle = 0$ for all~$A\in\ind(\cat) \ssm \add(\susp T)$.  But~$\langle x, [A] \rangle = \lambda_A$ by Lemma~\ref{lemm::bilinear-form}.  Thus~
 \[
  x = \sum_{i=1}^n \lambda_i [\susp T_i] = 0.
 \]
 But the~$[\susp T_i]$ are linearly independent in~$\Ksp(\cat)$.  Thus~$\lambda_i = 0$ for all~$i\in \{1, \ldots, n\}$.  This finishes the proof.
\end{proof}

\begin{proposition}
 Assume that~$\ind(\cat)$ is finite.  Then the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
\[
 z = x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
\]
Then for any~$B\in \ind{\cat}$, we have that
\[
 \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0, 
\]
where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.  Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.  This finishes the proof.
\end{proof}

\begin{corollary}
 If~$\ind(\cat)$ is finite, then the set
 \[
 \set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)} \cup \set{[\susp T_i]}{i=1, \ldots, n}
 \]
 is a basis of~$\Ksp(\cat)$.
\end{corollary}
\begin{proof}
 By Proposition~\ref{prop::free-set}, the set is free.  It suffices to prove that it generates~$\Ksp(\cat)$.  Let~$x\in \Ksp(\cat)$.  Consider
 \[
  z = x - \sum_{A\in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
 \]
 Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
\end{proof}

@@

\begin{proposition}
 Assume that the set~$\set{[\ell_A]}{A\in \ind(\cat) \ssm \add(\susp T)}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
\end{proposition}
\begin{proof}
 Let~$x\in \ker \b g$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support.  For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.

@@

\begin{remark}
Assume moreover that~$\cat$ is $\field$-linear and Ext-finite.
By the preliminary results of Section~\ref{subsection: prelim on extricats}, we can apply~\cite[Proposition 4.2]{IyamaNakaokaPalu} to obtain that~$\modt$ is Hom-finite.
In particular, if $\tc=\add T$, then $\End{\cat}(T)$ is a finite-dimensional~$\field$-algebra.
It thus also follows that Definition~\ref{defi::bilinear form} still makes sense in this more general settup: For any~$X,Y\in\cat$,
\[
\langle X,Y\rangle \eqdef \dim_\field \Hom{\tc}(FX,FY) = \dim_\field \cat/(\susp\tc)(X,Y).
\]
\end{remark}

When this makes sense, we make use of Notation~\ref{notation::ell_X}: if
\[
X \infl E \defl Y \dashrightarrow
\]
is an almost-split sequence (see~\cite{IyamaNakaokaPalu} for a definition in this setting), we let
\[
 \ell_X \eqdef [X]+[Y]-[E]\in\Ksp(\cat).
\]

\begin{theorem}\label{theorem::extricats}
Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation. Fix a conflation~$T\to 0 \to \susp T$. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
\[
L \eqdef \bigset{\ell_X}{X\in \ind(\cat) \ssm \add(\susp T)}
\]
generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}

\begin{corollary}
Assume that~$\ind(\cat)$ is finite.
Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
\end{corollary}
